Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-05-04 analysis/paper/paper.Rmd
I have fixed the facet compression problem! It is not(?) super reproducible but changes chunk options to manually expand the figure. Also added quick covariates to paper.rmd - definitly need cleaned up

```{r Fig-SurveyDates1, echo=FALSE, eval=TRUE, cache=FALSE, fig.show= 'asis', fig.cap="The first sighting of each species each year.", warning=FALSE}
print(plot_timing_1)
```

@@

```{r SpeciesTiming, eval=TRUE, cache = FALSE, include = FALSE}
# MADELEINE: write a script to extract, for just the target species listed at line 250, 
# just the dates each year that each of the target species was observed (somewhere in the survey areas - don't care which, at the moment)
# then add a layer to the ggplot 'Plot1' (horrid name, by the way) to visually distinguish those dates for that species.
# will have to play around to see if it is feasible to do this by faceting on the species or just make a separate 
# timing graph for each species - your call. It will be unreadable if try and put all of the target species on 
# a single plot

# tweak this call to source that new script, then un-comment, etc.
# source("../scripts/species_timing_EDA.R", echo=FALSE)

```{r Fig-SpeciesTiming, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap="For each of the target species, the dates on which they were observed in any of the sample areas."}

#edit to use the name of the new plot
#print(Plot1)
```

@@

>>>>

```{r Fig-SurveyDates1, echo=FALSE, eval=TRUE, cache=FALSE, fig.show= 'asis', fig.cap="The first sighting of each species each year.",fig.height=20, fig.width=12, warning=FALSE}
print(plot_timing_1)
```

@@

```{r Fig-SpeciesTiming2, echo=FALSE, eval=TRUE, cache=TRUE, fig.show= 'asis', fig.cap="For each of the target species, the dates on which they were observed in any of the sample areas."}

@@

```{r Covariates, eval=TRUE, cache = FALSE, include = FALSE}
source("../scripts/temp_covariates.R")
```
